Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-19 paper/supp-info.Rmd
remove supp info extra space
add loadd sensitivity_species_name it was not called before

```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}

fig_sensitivity_analysis_legend <- 
  paste0("Sensitivity analysis of environmental suitability error. ",
         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
         "The sensitivity analysis was performed by subsampling occurrences of", 
         " *", sensitivity_species_name$canonicalName, "* ", 
         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")

>>>>

```{r fig-sensitivity-analysis, fig.width = width('single'), fig.height = 2.2, fig.cap = fig_sensitivity_analysis_legend}
loadd(sensitivity_species_name)
fig_sensitivity_analysis_legend <- 
  paste0("Sensitivity analysis of environmental suitability error. ",
         "The number of independent occurrences retrieved from GBIF is inversely related to the error of environmental suitability for our plant-pollinator networks.", 
         "The sensitivity analysis was performed by subsampling occurrences of", 
         " *", sensitivity_species_name$canonicalName, "* ", 
         "the species in our dataset with the largest number of occurrences in GBIF, which was recorded in two of our communities.")
